---
title: "A03 EDA"
author: "dearbharat"
date: "6/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import Data
```{r warning=FALSE}
library(tidyverse)
lego <- read_csv("lego_sales.csv")
```

## 1- What are the three most common first names of customers?

```{r}
lego %>%
  select(first_name) %>%
  count(first_name) %>%
  arrange(desc(n))
```

2- What are the three most common themes of lego sets purchased?

```{r}
lego %>%
    select(theme) %>%
    count(theme) %>%
    arrange(desc(n))
```
## 3- Among the most common theme of lego sets purchased, what is the most common subtheme?

```{r}
lego %>%
    select(theme, subtheme) %>%
    filter(theme=="Star Wars" |
           theme=="Nexo Knights" |
           theme=="Gear" |
           theme=="Mixels") %>%
    count(subtheme) %>%
    arrange(desc(n))
```
## 4- Create a new variable called age_group and group the ages into the following categories: “18 and under”, “19 - 25”, “26 - 35”, “36 - 50”, “51 and over”. Be sure to save the updated data set so you can use the new variable in other questions.
```{r}
lego_age_group <- lego %>%
    mutate(age_group=case_when(
        age <= 18 ~ "18 and under" ,
        between(age, 19, 25) ~ "19 - 25" ,
        between(age, 26, 35) ~ "26 - 35" ,
        between(age, 36, 50) ~ "36 - 50" ,
        age >= 51 ~ "51 and over" ,
    ))
# To represent result:
lego_age_group %>%
    select(first_name, age ,age_group)
```
## 5- What is the probability a randomly selected customer 
### is in the 19 - 25 age group?
```{r}
lego_age_group  %>%
    count(age_group) %>%
    mutate(probablity=n/sum(n))
```
### is in the 19 - 25 age group and purchased a Duplo theme set?

```{r}
lego_age_group  %>%
        mutate(target_group=case_when(
            theme== "Duplo" & between(age, 19, 25) ~ 
            "Target Group" ,
            TRUE ~ "Not that group!")) %>% 
            # To represent result:
    select(theme ,age_group, target_group) %>% 
  # To represent result:
    count(target_group) %>%
    mutate(probablity=n/sum(n))
```
### is in the 19 - 25 age group given they purchased a Duplo theme set?

```{r}
lego_age_group  %>%
        filter(theme == "Duplo")  %>%
        mutate(target_group=case_when(
        between(age, 19, 25) ~ "purchased a Duplo an 19-25 age group" ,
        TRUE ~ "purchased a Duplo an NOT 19-25 age group"
             )) %>%

# To represent result:

    select(theme ,age_group, target_group) %>%

# To represent result:
     count(target_group) %>%
    mutate(probablity=n/sum(n))

```
## 6- Which age group has purchased the largest number of lego sets? How many did they purchase?

```{r}
new <- lego_age_group  %>%
    group_by(age_group)  %>%
    count(quantity)  %>%
    summarise(Number_of_Purchase=sum(n*quantity)) %>%
      arrange(desc(Number_of_Purchase))


new
```
## 7- Which age group has spent the most money on legos? How much did they spend?

```{r}
new1 <- lego_age_group %>%
    select(age_group, us_price, quantity) %>%
    group_by(age_group)  %>%
    summarise(Total=sum(quantity*us_price)) %>%
    arrange(desc(Total))

new1
```

## 8- Come up with a question you want to answer using this data, and write it down. Then, create a data visualization that answers the question, and briefly explain how your visualization answers the question.

I want to know the correlation between the “pieces” and “us_price”. For this purpose, categorize legos to four groups: “75 and under pieces”, “76 - 150 pieces”, “151 - 400 pieces”, “401 pieces and over”. first, show the number of each categories using bar and pie charts. In all plots:

### relevel x-axis parameter from fewest to largest number of pieces. (fct_relevel())

### delete NA elements from counting. (drop_na())

```{r}

lego_piece_price <- lego %>%
  select(pieces, us_price) %>%
    mutate(NumberOfPieces=case_when(
        pieces <= 75 ~ "Under 75 pieces" ,
        between(pieces, 76, 150) ~ "76 to 150 pieces" ,
        between(pieces, 151, 400) ~ "151 to 400 pieces" ,
        pieces >= 401 ~ "over 400 pieces")) %>%
    mutate(NumberOfPieces=fct_relevel(NumberOfPieces, 
                                    "Under 75 pieces",
                                    "76 to 150 pieces" ,
                                    "151 to 400 pieces" ,
                                    "over 400 pieces" )) %>%
                                   drop_na()


plot_ <- lego_piece_price %>%
  group_by(NumberOfPieces) %>%
 count()

ggplot(plot_, aes(NumberOfPieces, n))+
  geom_col()
```
